---
title: "Data import"
output: github_document
---

```{r}
library(tidyverse)
# what we want to use is the readr package -- to import data
```

## Read in some data
use path to open the data set(be specific)
there are two ways to open the files.
* absolute way(from the original folder)
* relative way(from your current working directory)
one good way of relative path is that anyone who copies this code and data and set their derectory the same way, the code still work.

Read in a litters dataset.

```{r}
litters_df = read.csv("./data/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
```

## take a look at the data

Printing in tge console
```{r}
litters_df
```

```{r}
#看前6行
head(litters_df)
#看后6行
tail(litters_df)
```

```{r}
#用a：：b可以跳过library的过程直接加载这个包里的这个package
#可以查看这个data frame里有多少rows、columns，有什么类型的数据，以及各类型数据的名称和总结
skimr::skim(litters_df)
```

更常用的：View function,打开一个新页面，显示这个data frame的信息

## OPTIONS TO READ csv

```{r}
litters_df = read.csv("./data/FAS_litters.csv", skip = 10, na = c("",".","999"))
```

check out `r `?read.csv()` for more information










